A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-03-16 index.Rmd
update title
rebuild book

---
title: "A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean"
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: "Mungbean.bib"
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---
# About
## Background  
A common practice for managing powdery mildew in mungbean is to couple fungicide with an insecticide spray early in the development of the crop, usually before the disease is detected. This is despite the current recommendations that the best yield protection is achieved when the fungicide is first applied at the first sign of the disease. These recommendations were based on individual studies, many of which lacked sufficient power to draw significant conclusions. We undertook a meta-analysis to determine, when should the first fungicide spray be applied on mungbean to maximise yield protection.

@@

## Acknowledgments  
This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia. Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), the Northern Grower Alliance. Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.

>>>>

---
title: "A meta-analysis of fungicide effects on mungbean powdery mildew"
author: "Paul Melloy, Emerson Del Ponte and Adam H. Sparks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: "Mungbean.bib"
biblio-style: apalike
link-citations: yes
github-repo: OpenPlantPathology/Mungbean_PM
description: "A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew."
---
# About
## Background  
A common practice for managing powdery mildew in mungbean is to couple fungicide with an insecticide spray early in the development of the crop, usually before the disease is detected. This is despite the current recommendations that the best yield protection is achieved when the fungicide is first applied at the first sign of the disease. These recommendations were based on individual studies, many of which lacked sufficient power to draw significant conclusions. We undertook a meta-analysis to determine, when should the first fungicide spray be applied on mungbean to maximise yield protection.

@@

## Acknowledgments  
This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia. Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), and the Northern Grower Alliance. Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.
